Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 \MakeLowercase{b}

### 2018-10-08 ms.tex
added Johanna's acknowledgement.

\section{Acknowledgements}
%Thanks to Alessondra Springman for good resources on core and mantle compositions and the gases that could sublimate off of them.
%MCMC fitting makes use of \texttt{emcee} \citep{foreman-mackey2013emcee} and the covariance plot was made with \texttt{corner.py} \citep{foremanCorner}.
The authors thank to Kento Masuda for sharing the 2015 Subaru spectrum of \shStar\ and giving helpful comments on this work.
Funding for E Schlawin is provided by NASA Goddard Spaceflight Center.
\added{This work was supported by Japan Society for Promotion of Science (JSPS) KAKENHI Grant Number JP16K17660.}
\replaced{The authors thank Benjamin Rackham for providing an estimate of the transit light source effect for a K4 V star and for helpful comments from Saul Rappaport.}{The authors thank Saul Rappaport for helpful comments.} % Now Ben is a coauthor
\added{This research has made use of the VizieR catalogue access tool, CDS, Strasbourg, France. The original description of the VizieR service was published in \citet{ochsenbein2000vizieR}.
This work has made use of data from the European Space Agency (ESA) mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}).
Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the {\it Gaia} Multilateral Agreement.
This publication makes use of data products from the Wide-field Infrared Survey Explorer, which is a joint project of the University of California, Los Angeles, and the Jet Propulsion Laboratory/California Institute of Technology, funded by the National Aeronautics and Space Administration.}

>>>>

\section{Acknowledgements}
%Thanks to Alessondra Springman for good resources on core and mantle compositions and the gases that could sublimate off of them.
%MCMC fitting makes use of \texttt{emcee} \citep{foreman-mackey2013emcee} and the covariance plot was made with \texttt{corner.py} \citep{foremanCorner}.
The authors thank to Kento Masuda for sharing the 2015 Subaru spectrum of \shStar\ and giving helpful comments on this work.
Funding for E Schlawin is provided by NASA Goddard Spaceflight Center.
\added{This work was supported by Japan Society for Promotion of Science (JSPS) KAKENHI Grant Number JP16K17660.
Support for this work was provided by NASA through Hubble Fellowship grant HST-HF2-51399.001 awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS5-26555.}
\replaced{The authors thank Benjamin Rackham for providing an estimate of the transit light source effect for a K4 V star and for helpful comments from Saul Rappaport.}{The authors thank Saul Rappaport for helpful comments.} % Now Ben is a coauthor
\added{This research has made use of the VizieR catalogue access tool, CDS, Strasbourg, France. The original description of the VizieR service was published in \citet{ochsenbein2000vizieR}.
This work has made use of data from the European Space Agency (ESA) mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}).
Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the {\it Gaia} Multilateral Agreement.
This publication makes use of data products from the Wide-field Infrared Survey Explorer, which is a joint project of the University of California, Los Angeles, and the Jet Propulsion Laboratory/California Institute of Technology, funded by the National Aeronautics and Space Administration.}
